\chapter{Electromagnetism}
\section{Fundamental Concepts}
\subsection{Charge, Current, Flux}
\begin{qt}
    \begin{center}
        Electric charge is conserved no matter how small our system is, even for elementary particle processes
    \end{center}
\end{qt}
\begin{qt}
    The total charge inside any volume $V$ is then given by the integral over the charge density:
    \begin{equation}
Q=\int_{V} d^{3} x \rho(\vec{x}, t)
\end{equation}
\end{qt}
Of course, \textbf{we can also use the charge density if there is only one charged object in our system.} In this case, the charge density is zero everywhere except at one specific point. Any integral over a region which contains the location of the object, yields simply the charge of the object. 
\begin{qt}
    Specifically, the charge density of a system with just one charged object located at $\vec{x}_{0}$ is
    \begin{equation}
\rho(\vec{x})=q \delta\left(\vec{x}-\vec{x}_{0}\right)
\end{equation}
\end{qt}
where $q$ is the charge of the object. Any integral over a region $V_{0}$ which contains $\vec{x}_{0}$ yields exactly $q,$ as it should be
$$
\begin{aligned}
\int_{V_{0}} d^{3} x \rho(\vec{x}, t) &=\int_{V_{0}} d^{3} x q \delta\left(\vec{x}-\vec{x}_{0}\right) \\
&=q \int_{V_{0}} d^{3} x \delta\left(\vec{x}-\vec{x}_{0}\right) \\
&=q
\end{aligned}
$$
\begin{qt}
    In electrodynamics, the \redp{the electric current} is defined as:
    \begin{equation}
I=\frac{d Q}{d t}
\end{equation}
\end{qt}
The correct tool to describe the flow of charges in three dimensions is called \textbf{\redp{current density}}. \bluep{A current density yields a vector at each point in space(i.e., vector space). The direction of the vector at a given point describes the direction of the flow. The length of the vector describes how much is flowing.}
\begin{qt}
    By introducing a vector $\vec{n}$ of unit length normal to a frame with area of $A$, we can calculate the current passing through the frame as:
    \begin{equation}
I \equiv \frac{\Delta Q}{\Delta t}=\rho_{0} A \vec{v}_{c} \cdot \vec{n}
\end{equation}
If we define \textbf{\redp{the electric current density}} as 
\begin{equation}
\vec{J} \equiv \rho_{0} \vec{v}_{c}
\end{equation}
we have
\begin{equation}
\vec{J} \cdot \vec{n} A=\rho_{0} \vec{v}_{c} \cdot \vec{n} A=I
\end{equation}
\end{qt}
In general, \textbf{the magnitude of the current density $|\vec{J}|$ at one specific point describes the amount of electric charge which passes per unit time through an infinitesimal surface element which is at right angles to the direction of the flow.} The direction of the charge density vector $\vec{J}$ encodes where the charges are flowing.

\begin{qt}
    If we want to know how much electric charge is flowing through a more complicated surface $S$, we have to calculate the \textbf{\redp{surface integral}}:
    \begin{equation}
I=\int_{S} \vec{J} \cdot \overrightarrow{d S}
\end{equation}
The total amount of charge passing through the surface $S$ during some time interval $\Delta t$ is then given by
\begin{equation}
\Delta Q=\Delta t \int_{S} \vec{J} \cdot \overrightarrow{d S}
\end{equation}
\end{qt}

\subsection{Electromagnetic Field}
An important feature of the electromagnetic field is that even a vector field is not sufficient and we need instead a tensor field. \textbf{The electromagnetic field tensor is an antisymmetric $(4 \times 4)$ matrix}
\begin{qt}
    \begin{equation}
F_{\mu \nu}(t, \vec{x})=\left(\begin{array}{cccc}
{0} & {F_{01}(t, \vec{x})} & {F_{02}(t, \vec{x})} & {F_{03}(t, \vec{x})} \\
{-F_{01}(t, \vec{x})} & {0} & {F_{12}(t, \vec{x})} & {F_{13}(t, \vec{x})} \\
{-F_{02}(t, \vec{x})} & {-F_{12}(t, \vec{x})} & {0} & {F_{23}(t, \vec{x})} \\
{-F_{03}(t, \vec{x})} & {-F_{13}(t, \vec{x})} & {-F_{23}(t, \vec{x})} & {0}
\end{array}\right)
\end{equation}
\redp{This tensor field, in some sense, assigns exactly two vectors to each point in space $\vec{x}$ at each point in time $t .$ }
\end{qt}
The vectors at each location represent the strength and direction of the electromagnetic field. It is conventional to introduce the electric vector field $\vec{E}(t, \vec{x})$ and the magnetic vector field $\vec{B}(t, \vec{x})$ and work with them, instead of with the electromagnetic tensor field $F_{\mu \nu}(t, \vec{x})$.
\begin{equation}
F_{\mu \nu}(t, \vec{x})\equiv\left(\begin{array}{cccc}
{0} & {-E_{1}(t, \vec{x}) / c} & {-E_{2}(t, \vec{x}) / c} & {-E_{3}(t, \vec{x}) / c} \\
{E_{1}(t, \vec{x}) / c} & {0} & {-B_{3}(t, \vec{x})} & {B_{2}(t, \vec{x})} \\
{E_{2}(t, \vec{x}) / c} & {B_{3}(t, \vec{x})} & {0} & {-B_{1}(t, \vec{x})} \\
{E_{3}(t, \vec{x}) / c} & {-B_{2}(t, \vec{x})} & {B_{1}(t, \vec{x})} & {0}
\end{array}\right)
\end{equation}
\bluep{Each of these two fields $\vec{E}(t, \vec{x})=\left(E_{1}(t, \vec{x}), E_{2}(t, \vec{x}), E_{3}(t, \vec{x})\right)^{T}$
and $\vec{B}(t, \vec{x})=\left(B_{1}(t, \vec{x}), B_{2}(t, \vec{x}), B_{3}(t, \vec{x})\right)^{T}$ assigns a vector to each point in space $\vec{x}$ at each point in time $t$}.

Unfortunately, the interpretation of the electric field $\vec{E}(t, \vec{x})$ and the magnetic field $\vec{B}(t, \vec{x})$ is not so simple. Instead, the little arrows encode information about the somewhat abstract "physical field", which we can understand as follows: \redp{The direction of the vector at a given location encodes in which direction a test charge would move if it were placed here. The magnitude of the vector encodes how fast the test charge would accelerate as a result of, for example, the electric field}. In this sense, these more abstract fields encode how something would
flow if it were there.
\begin{qt}
    In practice the electric field strength at a point is measured by placing a small test charge at that point and measuring the force on it:
    \begin{equation}
\vec{E}(\vec{x}) \equiv \frac{\vec{F}(\vec{x})}{q}
\end{equation}
\end{qt}
\subsection{Electromagnetic potential}
For the moment, we only note that the electromagnetic potential is characterized by 4 numbers at each point in space and time $A_{\mu}(t, \vec{x})=\left(A_{0}(t, \vec{x}), A_{1}(t, \vec{x}), A_{2}(t, \vec{x}), A_{3}(t, \vec{x})\right)^{T}$ and that the electric and magnetic fields can be calculated immediately once the electromagnetic potential is specified:
\begin{qt}
    \begin{equation}
\begin{aligned}
&E_{i}=\left(-\partial_{i} A_{0}-\partial_{0} A_{i}\right) / c\\
&B_{i}=\epsilon_{i j k} \partial_{j} A_{k}
\end{aligned}
\end{equation}
where $i, j, k \in\{1,2,3\} .$ We can also write this as a vector equations
\begin{equation}
\begin{aligned}
&\vec{E}=\left(-\nabla A_{0}-\partial_{t} \vec{A}\right) / c\\
&\vec{B}=\nabla \times \vec{A}
\end{aligned}
\end{equation}
\end{qt}
We can also express the tensor field itself using the electromagnetic potential
\begin{qt}
    \begin{equation}
F_{\mu v}=\partial_{\mu} A_{v}-\partial_{v} A_{\mu}
\end{equation}
\end{qt}

\section{Fundamental Equations}
The Lorentz force law describes how charged object react to the presence of the electric and magnetic field. Maxwell's equations describe how non-zero electric and magnetic field strengths are generated by charges and currents. Moreover, they also describe how the electric and magnetic fields influence each other. In addition, the continuity equation encodes the fact that electric charge is conserved. All this is summarized by the following diagram:
\begin{qt}
    \begin{center}
        


\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Straight Lines [id:da6043751763886723] 
\draw    (177,53.47) -- (394,53.47) ;
\draw [shift={(397,53.47)}, rotate = 180] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
\draw [shift={(174,53.47)}, rotate = 0] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
%Straight Lines [id:da07068797370513968] 
\draw    (168,163.47) -- (400,163.47) ;
\draw [shift={(403,163.47)}, rotate = 180] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
\draw [shift={(165,163.47)}, rotate = 0] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
%Curve Lines [id:da13680905709879954] 
\draw    (119,152.47) .. controls (141.6,135.52) and (216.12,101.05) .. (300.33,103.47) .. controls (380.34,105.76) and (438.25,137.2) .. (455.03,149.66) ;
\draw [shift={(457.33,151.47)}, rotate = 219.81] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;

%Curve Lines [id:da32747829322015765] 
\draw    (119,178.38) .. controls (137.27,189.89) and (205.75,210.19) .. (285.33,212.47) .. controls (369.55,214.88) and (443.33,185.47) .. (461.33,174.47) ;

\draw [shift={(116.33,176.47)}, rotate = 40.24] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;
%Straight Lines [id:da5861609067826448] 
\draw    (458.33,245.47) -- (458.33,176.47) ;
\draw [shift={(458.33,174.47)}, rotate = 450] [color={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.75]    (10.93,-3.29) .. controls (6.95,-1.4) and (3.31,-0.3) .. (0,0) .. controls (3.31,0.3) and (6.95,1.4) .. (10.93,3.29)   ;

%Curve Lines [id:da35984262406569245] 
\draw    (470.33,151.47) .. controls (509.53,122.07) and (486.31,98.43) .. (459.01,67.38) ;
\draw [shift={(457.33,65.47)}, rotate = 408.81] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;

%Curve Lines [id:da050391804224369396] 
\draw    (432.33,65.47) .. controls (407.83,74.29) and (405.42,118.64) .. (437.34,149.59) ;
\draw [shift={(439.33,151.47)}, rotate = 222.36] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;

%Curve Lines [id:da7848731503908734] 
\draw    (102.33,152.47) .. controls (59.21,124.05) and (68.92,111.95) .. (88.14,69.13) ;
\draw [shift={(89.33,66.47)}, rotate = 473.96] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;

%Curve Lines [id:da2947796011268943] 
\draw    (142.33,66.47) .. controls (170.61,81.09) and (166.56,119.48) .. (150.59,150.13) ;
\draw [shift={(149.33,152.47)}, rotate = 298.74] [fill={rgb, 255:red, 0; green, 0; blue, 0 }  ][line width=0.08]  [draw opacity=0] (10.72,-5.15) -- (0,0) -- (10.72,5.15) -- (7.12,0) -- cycle    ;


% Text Node
\draw    (67.5,41) -- (172.5,41) -- (172.5,65) -- (67.5,65) -- cycle  ;
\draw (120,53) node   [align=left] {electric charge};
% Text Node
\draw    (397,41) -- (503,41) -- (503,65) -- (397,65) -- cycle  ;
\draw (450,53) node   [align=left] {electric current};
% Text Node
\draw    (77.5,153) -- (164.5,153) -- (164.5,177) -- (77.5,177) -- cycle  ;
\draw (121,165) node   [align=left] {electric field};
% Text Node
\draw    (403,152) -- (503,152) -- (503,176) -- (403,176) -- cycle  ;
\draw (453,164) node   [align=left] {magnetic field};
% Text Node
\draw    (377.5,247) -- (516.5,247) -- (516.5,271) -- (377.5,271) -- cycle  ;
\draw (447,259) node   [align=left] {no magnetic charge};
% Text Node
\draw (291,44) node   [align=left] {continuity equation};
% Text Node
\draw (281,152) node   [align=left] {wave equations};
% Text Node
\draw (292,119) node   [align=left] {Ampere-Maxwell law};
% Text Node
\draw (299,225) node   [align=left] {Faraday's law};
% Text Node
\draw (479,222) node   [align=left] {magnetic field Gauss law};
% Text Node
\draw (496,123) node  [font=\small,rotate=-0.65] [align=left] {Lorentz force law};
% Text Node
\draw (374,85) node  [font=\small] [align=left] {Ampere-Maxwell law};
% Text Node
\draw (184,87) node  [font=\small] [align=left] {electric field Gauss law};
% Text Node
\draw (76,119) node  [font=\small,rotate=-0.65] [align=left] {Lorentz force law};


\end{tikzpicture}

    \end{center}
\end{qt}
\subsection{Continuity equation}
\begin{qt}
    \begin{equation}
\frac{\partial}{\partial t} \int_{V} \rho d V=\oint_{S} \vec{J} \cdot \overrightarrow{d S}
\end{equation}
\end{qt}
The continuity equation really describes the local conservation of electric charge. In words, the continuity equation tells us: \bluep{the at which the charge density changes in a given volume is exactly equal to the net amount of electric charge flowing through the surface of the volume per unit time.}

Using Gauss's theorem, we have
\begin{equation}
\oint_{S} \vec{J} \cdot \overrightarrow{d S}=\int_{V} \nabla \cdot \vec{J} d V
\end{equation}
and we get the \textbf{differential form of the continuity equation}
\begin{qt}
    \begin{equation}
\frac{\partial}{\partial t} \rho-\nabla \cdot \vec{J}=0
\end{equation}
\end{qt}
\subsection{Lorentz force law}
\begin{qt}
    \begin{equation}
\vec{F}_{E}=q \vec{E}
\end{equation}
\begin{equation}
\vec{F}_{B}=q \vec{v} \times \vec{B}
\end{equation}
\end{qt}
The Lorentz force law consists of two parts. The first part, tells us that the force resulting from the electric field $\vec{E}$ is directly proportional to $\vec{E}$. The second part take into account that only moving charged objects react to the presence of the magnetic field. When the velocity $\vec{v}$ is completely perpendicular to the magnetic field $\vec{B}$, the trajectory is simply a circle.

The general Lorentz force law therefore reads
\begin{qt}
    \begin{equation}
\vec{F}=q(\vec{E}+\vec{v} \times \vec{B})
\end{equation}
\end{qt}

\subsection{Gauss's law for the electric field}
\textbf{\redp{Each electric charge generates a particular structure in the electromagnetic field and this, in turn, has a direct impact on other charges}}.

We first introduce the \textbf{flux of the electric field through some surface $S$}:
\begin{equation}
\phi \equiv \int_{S} \vec{E} \cdot \overrightarrow{d S}
\end{equation}
Our goal is to find an equation which describes that \textbf{a nonzero charge within some volume has a direct impact on the structure of the electric field}. The charge within some volume $V$ is given by $\int_{V} \rho d V$ and we just argued that \redp{\textbf{a reasonable object represent the electric field in such an equation is the flux of
the electric field}}:
\begin{qt}
    \begin{equation}
\oint_{S} \vec{E} \cdot \overrightarrow{d S}=\frac{1}{\epsilon_{0}} \int_{V} \rho d V
\end{equation}
\end{qt}
where $\epsilon_{0}$ is a constant known as \textbf{electric permittivity} which \textit{describes how strongly the electric field reacts to the presence of charges}. This is the integral form of Gauss's law for electric fields. In words, it tells us:
\begin{qt}
    The flux of the electric field passing through a closed surface is directly proportional to the amount of electric charge contained inside the surface.
\end{qt}
\bluep{Note that "flux" here is simply a statement about the \textbf{length of the vectors at the boundary of our volume.} Moreover, if the sign of the flux is positive, the vectors point outwards and \textit{vice versa}}.
\begin{qt}
    \begin{itemize}
        \item $\vec{J}$ and $\vec{E}$ assign a vector to each point in space.
        \item For $\vec{J}$ these vectors represent the real movement of our electric charges. For the more abstract electric field $\vec{E},$ the arrows only represent how a charge would move if it were there.
        
    \end{itemize}
\end{qt}

Using Gauss's theorem, we also have \textbf{the differential form of Gauss's law for the electric field}:
\begin{qt}
    \begin{equation}
\nabla \cdot \vec{E}=\frac{\rho}{\epsilon_{0}}
\end{equation}
\end{qt}
\textit{\textbf{In general, the divergence of a vector field gives us information about the tendency of the field to flow towards or away from a specific point.}} With this in mind, we can say that the differential form of Gauss’s law for the electric field tells us:
\begin{qt}
    The structure of the electric field generated by electric charges is such that it converges upon negative charges and diverges from positive charges.
\end{qt}
The integral form is especially useful for macroscopic problems
which posses a high degree of symmetry, e.g. when there is a rotationally symmetric charge distribution. The differential form is useful, for example, when we want to talk about electromagnetic waves.
\subsection{Gauss's law for the magnetic field}
So far no non-zero magnetic
charge density has ever been observed, and \textbf{the integral form of Gauss's law for the magnetic field} reads
\begin{qt}
    \begin{equation}
\oint_{S} \vec{B} \cdot \overrightarrow{d S}=0
\end{equation}
\end{qt}
Thus, this equation tells us
\begin{qt}
    The flux of the magnetic field passing through any closed surface is zero.
\end{qt}
Again, \textbf{the differential form is}
\begin{qt}
    \begin{equation}
\nabla \cdot \vec{B}=0
\end{equation}
Since the right-hand side of our equation is zero, we can conclude that\textbf{ the tendency of the magnetic field to flow towards a point P is always exactly equal to its tendency to flow away from P. Any "inflow" of the magnetic field is always accompanied by an "outflow" of exactly the same magnitude.}
\end{qt}
\bluep{If the divergence is non-zero, the structure was created by a fundamental charge. If the divergence is zero, the structure was created by a different field (or a current).}

The non-zero magnetic field strengths generated by conventional magnets are generated by the billions of individual electrons which exist inside any macroscopic object. \textbf{\bluep{Each electron orbits around a nucleus and possesses a non-zero internal angular momentum}}. The special thing about magnets is that in these objects \textbf{\bluep{the majority of electrons rotate around approximately the same axis}}.

Note that \textbf{\redp{we can also achieve a non-zero electric field with zero divergence.} This is described by Faraday's law. The structure of the electric field generated by a changing magnetic field circulates back on itself}.

\subsection{Faraday's law}
We want a description in which a non-zero electric field strength shows up when the magnetic field is changing. The correct mathematical notion this task are time-derivatives. If the time-derivative of the magnetic field is non-zero, this means that the magnetic field is changing over time. Hence, our first puzzle piece is
$$
\dots=\int_{S} \frac{\partial}{\partial t} \vec{B} \cdot \overrightarrow{d S}
$$
The second puzzle piece that we need is something which describes the structure of the electric field that results from such a changing magnetic field.

A first hint is that the left-hand side must depend on our choice of the surface $S$ too. However, a volume integral over $\vec{E}$ is not a good idea since then $S$ would represent the surface of the volume. As a result $S$ would be a closed surface and, as mentioned above, Gauss's law for the magnetic field tells us that the integral over the magnetic field for any closed surface vanishes. Thus we use the boundary of a surface:
\begin{qt}
    \begin{equation}
\oint_{\mathrm{C}} \vec{E} \cdot \overrightarrow{d l}=-\int_{S} \frac{\partial}{\partial t} \vec{B} \cdot \overrightarrow{d S}
\end{equation}
The contour integral of LHS describes the circulation of the electric field. The minus sign encodes in which direction the resulting electric field circulates.
\end{qt}
To summarize, Faraday's law tells us
\begin{qt}
    A changing magnetic field flux generates a circulating structure in the electric field.
\end{qt}
\begin{mybox}
What's the physical meaning of a contour integral like $\oint_{C} \vec{E} \cdot \overrightarrow{d l}$?
\end{mybox}
\begin{mybox2}
From Lorentz force laws, we have 
$$
\begin{aligned}
\oint_{C} \vec{E} \cdot \overrightarrow{d l} &=\oint_{C} \frac{\vec{F}}{q} \cdot \overrightarrow{d l} \\
&=\frac{1}{q} \oint_{C} \vec{F} \cdot \overrightarrow{d l} \\
& \equiv \frac{W}{q}
\end{aligned}
$$
where$W$ denotes the work done by the electric field if we move a test charge $q$ along the path $C$.

\textbf{Therefore, we can conclude that the circulation of the electric field represents the energy for each unit of charge moving along the contour C.}
\end{mybox2}
Here, \redp{we use Stokes' theorem to derive the differential form of Faraday's theorem.}
\begin{equation}
\oint_{C} \vec{E} \cdot \overrightarrow{d l}=\int_{S} \nabla \times \vec{E} \cdot \overrightarrow{d S}
\end{equation}
\begin{qt}
    \begin{equation}
\nabla \times \vec{E}=-\frac{\partial}{\partial t} \vec{B}
\end{equation}
\end{qt}
\subsection{Ampere-Maxwell law}
\bluep{The Ampere-Maxwell law describes how a changing electric field generates a non-zero magnetic field strength}.\textbf{A non-zero magnetic field strength can be generated through
a changing electric field. We can also generate a non-zero magnetic field strength using moving electric charge.} Thus the integral form of the Ampere-Maxwell law reads
\begin{qt}
    \begin{equation}
\oint_{C} \vec{B} \cdot \overrightarrow{d l}=\mu_{0}\left(I_{\mathrm{enc}}+\epsilon_{0} \int_{S} \frac{\partial}{\partial t} \vec{E} \cdot \overrightarrow{d S}\right)
\end{equation}
$\mu_{0}$ and $\epsilon_{0}$ are proportionality constants known as vacuum permeability and vaccum permittivity. Moreover, $I_{enc}$ denotes the electric current enclosed by the contour $C$.
\end{qt}
By using Stokes' theorem, we find
$$
\begin{aligned}
\oint_{C} \vec{B} \cdot \overrightarrow{d l} &=\mu_{0}\left(I_{\mathrm{enc}}+\epsilon_{0} \int_{S} \frac{\partial}{\partial t} \vec{E} \cdot \overrightarrow{d S}\right) \\
\int_{S} \nabla \times \vec{B} \cdot \overrightarrow{d S} &=\mu_{0}\left(I_{\mathrm{enc}}+\epsilon_{0} \int_{S} \frac{\partial}{\partial t} \vec{E} \cdot \overrightarrow{d S}\right) \\
\int_{S} \nabla \times \vec{B} \cdot \overrightarrow{d S} &=\mu_{0}\left(\int_{S} \overrightarrow{J} \overrightarrow{d S}+\epsilon_{0} \int_{S} \frac{\partial}{\partial t} \vec{E} \cdot \overrightarrow{d S}\right) \\
\int_{S} \nabla \times \vec{B} \cdot \overrightarrow{d S} &=\mu_{0} \int_{S}\left(\vec{J}+\epsilon_{0} \frac{\partial}{\partial t} \vec{E}\right) \cdot \overrightarrow{d S}
\end{aligned}
$$
And \textbf{the differential form of the Ampere-Maxwell law} becomes
\begin{qt}
\begin{equation}
\nabla \times \vec{B}=\mu_{0}\left(\vec{J}+\epsilon_{0} \frac{\partial}{\partial t} \vec{E}\right)
\end{equation}
\end{qt}

\subsection{The wave equations}
To derive the equation of motion for the electric field $\overrightarrow{E}$, we start by taking the curl on both sides of Faraday's law:
$$
\begin{aligned}
\nabla \times \vec{E} &=-\frac{\partial}{\partial t} \vec{B} \\
\nabla \times \nabla \times \vec{E} &=-\nabla \times \frac{\partial}{\partial t} \vec{B} \\
\nabla \times \nabla \times \vec{E} &=-\frac{\partial}{\partial t} \nabla \times \vec{B}
\end{aligned}
$$
Using the follwoing vector identity
\begin{qt}
\begin{equation}
\nabla \times \nabla \times \vec{E}=\nabla(\nabla \cdot \vec{E})-\nabla^{2} \vec{E}
\end{equation}
\end{qt}
We have:
$$
\begin{aligned}
\nabla \times \nabla \times \vec{E} &=-\frac{\partial}{\partial t} \nabla \times \vec{B} \\
\nabla(\nabla \cdot \vec{E})-\nabla^{2} \vec{E} &=-\frac{\partial}{\partial t} \nabla \times \vec{B} \\
\nabla(\nabla \cdot \vec{E})-\nabla^{2} \vec{E} &=-\frac{\partial}{\partial t}\left(\mu_{0}\left(\vec{J}+\epsilon_{0} \frac{\partial}{\partial t} \vec{E}\right)\right)
\end{aligned}
$$
Gauss's law for the electric field reads $\nabla \cdot \vec{E}=\frac{\rho}{\epsilon_{0}}$, we have
$$
\nabla\left(\frac{\rho}{\epsilon_{0}}\right)-\nabla^{2} \vec{E}=-\frac{\partial}{\partial t}\left(\mu_{0}\left(\vec{J}+\epsilon_{0} \frac{\partial}{\partial t} \vec{E}\right)\right)
$$
And finally, we obtain \textbf{the wave equation for the electric field}
\begin{qt}
\begin{equation}
\nabla^{2} \vec{E}=\mu_{0} \epsilon_{0} \frac{\partial^{2}}{\partial t^{2}} \vec{E}
\label{waveEqElectric}
\end{equation}
\end{qt}
By following completely analogues steps, we have
\textbf{the wave equation for the magnetic field} as
\begin{qt}
\begin{equation}
\nabla^{2} \vec{B}=\mu_{0} \epsilon_{0} \frac{\partial^{2}}{\partial t^{2}} \vec{B}
\end{equation}
\end{qt}

So in summary, 
static charged object $\rightarrow$ static radial electric field

moving charged object $\rightarrow$ static circulating magnetic field

changing magnetic field $\rightarrow$ changing circulating electric field 

changing electric field $\rightarrow$ changing circulating magnetic field.

\section{Eletrostatics and Magnetostatics}
If the charge density is static $\left(\partial_{t} \rho=0\right),$ the resulting electric field configuration is time-independent. Analogously, if our current is steady $\left(\partial_{t} \vec{J}=0\right),$ the resulting magnetic field configuration is time-independent.

\bluep{In such systems we can treat the electric field and the magnetic field independently} because only if the electric field is changing does it have an effect on the magnetic field and vice versa.

For the electric field, we have
\begin{qt}
\begin{equation}
\begin{aligned}
\nabla \cdot \vec{E} &=\frac{\rho}{\epsilon_{0}} \\
\nabla \times \vec{E} &=0
\end{aligned}
\label{electrostatic}
\end{equation}
\end{qt}
The general solution to the electrostatic equations in (\ref{electrostatic}) is known as \redp{Coulomb's law}
\begin{qt}
\begin{equation}
\vec{E}(\vec{r})=\frac{1}{4 \pi \epsilon_{0}} \int \frac{\rho(\vec{r})\left(\vec{r}-\vec{r}^{\prime}\right)}{\left|\vec{r}-\vec{r}^{\prime}\right|^{3}} d^{3} \vec{r}^{\prime}
\label{coulombLaw}
\end{equation}
If we writing our charge distribution in terms of individual charges
$$
\rho(\vec{r})=\sum_{i} q_{i} \delta\left(\vec{r}-\vec{r}_{i}\right)
$$
we have
$$
\vec{E}(\vec{r})=\frac{1}{4 \pi \epsilon_{0}} \int \frac{\rho(\vec{r})\left(\vec{r}-\vec{r}^{\prime}\right)}{\left|\vec{r}-\vec{r}^{\prime}\right|^{3}} d^{3} \vec{r}^{\prime}=\sum_{i} \frac{q_{i}}{4 \pi \epsilon_{0}} \frac{\vec{r}-\vec{r}_{i}}{\left|\vec{r}-\vec{r}_{i}\right|^{3}}
$$
\end{qt}
For the magnetic field
\begin{qt}
\begin{equation}
\begin{aligned}
\nabla \cdot \vec{B} &=0 \\
\nabla \times \vec{B} &=\mu_{0} \vec{J}
\end{aligned}
\end{equation}
The solution has form of
\begin{equation}
\vec{B}(\vec{r})=\frac{\mu_{0}}{4 \pi} \int \frac{\vec{J}\left(\vec{r}^{\prime}\right) \times\left(\vec{r}-\vec{r}^{\prime}\right)}{\left|\vec{r}-\vec{r}^{\prime}\right|^{3}} d^{3} r^{\prime}
\label{Biot-SavartLaw}
\end{equation}
This is known as \textbf{Biot-Savart law}. It tells us that the magnetic field configuration generated by a general current density is simply the sum over the field configurations generated by the individual moving charges:
$$
\vec{J}(\vec{r})=\sum_{i} q_{i} \delta\left(\vec{r}-\vec{r}_{i}\right) \vec{v}_{i}
$$
Putting this into \ref{Biot-SavartLaw}
$$
\vec{B}(\vec{r})=\sum_{i} \frac{\mu_{0} q_{i}}{4 \pi} \vec{v}_{i} \times \frac{\vec{r}-\vec{r}_{i}}{\left|\vec{r}-\vec{r}_{i}\right|^{3}}
$$
\end{qt}
\subsection{Electric field of a single point charge}
Single point charge $\rho(\vec{r})=q \delta(\vec{r})$, using Gauss's law
$$
\oint_{S} \vec{E} \cdot \overrightarrow{d S}=\frac{1}{\epsilon_{0}} \int_{V} \rho d V
$$
$$
\int_{S} \vec{E} \cdot \overrightarrow{d S}=\frac{q}{\epsilon_{0}} \underbrace{\int_{V} \delta(\vec{r}) d V}_{=1}
$$
$$
\int_{S} \vec{E} \cdot \overrightarrow{d S}=\frac{q}{\epsilon_{0}}
$$
$$
\int_{0}^{2 \pi} \int_{0}^{\pi} E \underbrace{\vec{e}_{r} \cdot \vec{e}_{r}} r^{2} \sin (\theta) d \theta d \phi=\frac{q}{\epsilon_{0}}
$$
Thus,
$$
E=\frac{q}{r^{2} 4 \pi \epsilon_{0}}
$$
And the \textbf{Coulomb potential} is 
\begin{qt}
\begin{equation}
\phi=\frac{Q q}{r 4 \pi \epsilon_{0}}
\label{coulombPotential}
\end{equation}
\end{qt}
\subsection{Electric field of a sphere}
charge distribution reads
$$
\rho(\vec{r})=\left\{\begin{array}{ll}
{\rho_{0},} & {\text { on the sphere: }|\vec{r}|=R} \\
{0,} & {\text { otherwise }}
\end{array}\right.
$$
Thus,
$$
\vec{E}(\vec{r})=0 \quad \text { for }|\vec{r}|<R
$$
and
$$
\vec{E}(\vec{r})=\frac{\rho_{0}}{4 \pi \epsilon_{0}} \int \frac{\delta\left(\left|\vec{r}^{\prime}\right|-R\right)\left(\vec{r}-\vec{r}^{\prime}\right)}{\left|\vec{r}-\vec{r}^{\prime}\right|^{3}} d^{3} r^{\prime}=\frac{\rho_{0}}{4 \pi \epsilon_{0}} \int_{0}^{2 \pi} \int_{0}^{\pi} \int_{0}^{\infty} \frac{\delta\left(\left|\vec{r}^{\prime}\right|-R\right)\left(\vec{r}-\vec{r}^{\prime}\right)}{\left|\vec{r}-\vec{r}^{\prime}\right|^{3}} r^{\prime 2} d r^{\prime} \sin (\theta) d \phi d \theta
$$
Thus, outside of the sphere the electric field is described by
$$
\vec{E}(\vec{r})=\frac{q}{4 \pi \epsilon_{0} r^{2}} \vec{e}_{r}
$$
\subsection{Electric field of an electric dipole}
For simplicity, we assume that we are dealing with two point charges and choose our coordinate system such that one charge sits at the origin. The charge density then reads
$$
\rho(\vec{x})=q \delta(\vec{x})-q \delta(\vec{x}-\vec{d})
$$
where $\vec{d}$ is a vector pointing from the charge at the origin to the second charge. We can now immediately write down the resulting electric field configuration because we know that we simply have to \textbf{use a superposition of the individual configurations}.
\begin{qt}
\begin{equation}
\vec{E}(r)=\vec{E}_{q}(r)+\vec{E}_{-q}(r)=\frac{q \vec{r}}{4 \pi \epsilon_{0}|\vec{r}|^{3}}-\frac{q(\vec{r}-\vec{d})}{4 \pi \epsilon_{0}|\vec{r}-\vec{d}|^{3}} \vec{e}_{r}
\end{equation}
\end{qt}
\subsection{Electric field of more complicated charge distributions}
The general formula for the electric potential is
\begin{equation}
\phi(\vec{r})=\frac{1}{4 \pi \epsilon_{0}} \int \frac{\rho\left(\vec{r}^{\prime}\right)}{\left|\vec{r}-\vec{r}^{\prime}\right|} d^{3} r^{\prime}
\label{generalElectricPotential}
\end{equation}
We assume that the charge distribution $\rho\left(\vec{r}^{\prime}\right)$ is localized within some region $V .$ In mathematical terms, being far away from our charge distribution then means $|\vec{r}| \gg\left|\vec{r}^{\prime}\right|$ for all $\vec{r}^{\prime}$ in $V$

The main idea is that \textbf{we can then use \redp{Taylor expansion to simplify the general formula (\ref{generalElectricPotential})}}. In particular, we need the expansion
\begin{equation}
\begin{aligned}
\frac{1}{\left|\vec{r}-\vec{r}^{\prime}\right|} &=\frac{1}{r}-\vec{r}^{\prime} \cdot \nabla \frac{1}{r}+\ldots \\
&=\frac{1}{r}+\vec{r}^{\prime} \cdot \frac{\vec{r}}{r^{3}}+\ldots
\end{aligned}
\end{equation}
and
\begin{equation}
\begin{aligned}
\phi(\vec{r})=& \frac{1}{4 \pi \epsilon_{0}} \int \rho\left(\vec{r}^{\prime}\right) \frac{1}{\left|\vec{r}-\vec{r}^{\prime}\right|} d^{3} r^{\prime} \\
=& \frac{1}{4 \pi \epsilon_{0}} \int \rho\left(\vec{r}^{\prime}\right)\left(\frac{1}{r}+\vec{r}^{\prime} \cdot \frac{\vec{r}}{r^{3}}+\ldots\right) d^{3} r^{\prime} \\
=& \frac{1}{4 \pi \epsilon_{0} r} \int \rho\left(\vec{r}^{\prime}\right) d^{3} r^{\prime} \\
&+\frac{1}{4 \pi \epsilon_{0} r^{3}} \int \rho\left(\vec{r}^{\prime}\right) \vec{r}^{\prime} \cdot \vec{r} d^{3} r^{\prime}+\ldots
\end{aligned}
\end{equation}
\bluep{If we are sufficiently far away}, we can approximate our general formula as
$$
\phi(\vec{r}) \approx \frac{q}{4 \pi \epsilon_{0} r}
$$
\bluep{If we look closely enough}, we should describe the potential using
$$
\phi(\vec{r}) \approx \frac{q}{4 \pi \epsilon_{0} r}+\frac{1}{4 \pi \epsilon_{0} r^{3}} \int \rho\left(\vec{r}^{\prime}\right) \vec{r}^{\prime} \cdot \vec{r} d^{3} r^{\prime}
$$
where we can define
\begin{qt}
the \textbf{dipole moment}
\begin{equation}
\vec{p} \equiv \int \rho\left(\vec{r}^{\prime}\right) \vec{r}^{\prime} d^{3} r^{\prime}
\label{dipoleMoment}
\end{equation}
And the potential then reads
$$
\phi(\vec{r}) \approx \frac{q}{4 \pi \epsilon_{0} r}+\frac{1}{4 \pi \epsilon_{0} r^{3}} \vec{p} \cdot \vec{r}
$$
\end{qt}
Analogously it’s possible to introduce additional quantities which characterize the higher order terms in the Taylor expansion.
For example,
$$
\phi(\vec{r}) \approx \frac{1}{4 \pi \epsilon_{0}}\left(\frac{q}{r}+\frac{\vec{p} \cdot \vec{r}}{r^{3}}+\sum_{i j} \frac{Q_{i j} r_{i} r_{j}}{2 r^{5}}\right)
$$
where we have
\begin{qt}
the quadrupole moment defined as
\begin{equation}
Q_{i j} \equiv \int_{V} \rho\left(\vec{r}^{\prime}\right)\left(3 r_{i}^{\prime} r_{j}^{\prime}-\delta_{i j} r^{\prime 2}\right) d^{3} r^{\prime}
\label{quadrupoleMoment}
\end{equation}
\end{qt}
\redp{This method of collecting step-by-step information about complicated charge distributions is known as \textbf{multipole expansion}.}

\subsection{Boundary Value Problem}
Finding a description of electrostatic systems where the charge distribution is not fixed and known is usually called a boundary value problem. The main task in all these problems is to \textbf{solve the integral in Coulomb’s law}.

In the context of boundary value problems it is often more convenient to use the electric potential instead of the electric field. The correct electrostatic equation for the electric potential can be derived using Maxwell's equations and the relation between the potential $\phi$ and the electric field $\vec{E}$:
\begin{qt}
\begin{equation}
\begin{aligned}
\nabla \cdot \vec{E} &=\frac{\rho}{\epsilon_{0}} \\
-\nabla^{2} \phi &=\frac{\rho}{\epsilon_{0}}
\end{aligned}
\end{equation}
\end{qt}
There are clever methods for solving the Poisson equation. The main idea behind the most famous one is that \textbf{\bluep{we can calculate the solution for a general charge distribution by using the known solutions for individual charges}}. Hence, the basic building block for a general solution is the solution for a single point charge. The charge distribution of a single point charge at $\vec{r}^{\prime}$ is $\rho(\vec{r}) \sim \delta\left(\vec{r}-\vec{r}^{\prime}\right)$

Therefore, our main task in constructing a general solution is to solve the equation:
\begin{equation}
\nabla^{2} G\left(\vec{r}, \vec{r}^{\prime}\right)=\delta\left(\vec{r}-\vec{r}^{\prime}\right)
\end{equation}
The solution $G\left(\vec{\tau}, \vec{r}^{\prime}\right)$ is known as the Green's function for the Laplacian operator $\nabla^{2} \equiv \Delta .$ The Green’s function for the Laplacian operator reads
\begin{equation}
G\left(\vec{r}, \vec{r}^{\prime}\right)=\frac{1}{4 \pi} \frac{1}{\left|\vec{r}-\vec{r}^{\prime}\right|}
\end{equation}
The main idea is that as soon as we have the solution $G\left(\vec{r}, \vec{r}^{\prime}\right)$ for a single point charge, \textbf{we can calculate directly the solution of the Poisson equation for a general charge distribution $\rho\left(\vec{r}^{\prime}\right)$ as follows:}
\begin{qt}
\begin{equation}
\phi_{\mathrm{sol}}(\vec{r})=\frac{1}{\epsilon_{0}} \int \rho\left(\vec{r}^{\prime}\right) G\left(\vec{r}, \vec{r}^{\prime}\right) d^{3} r^{\prime}
\end{equation}
\end{qt}

\subsection{Magnetic field of a wire}
The Ampere-Maxwell law tells us:
\begin{equation}
\oint_{C} \vec{B} \cdot \overrightarrow{d l}=\mu_{0} \int_{S} \vec{J} \cdot \overrightarrow{d S}
\end{equation}
Since
$$
\begin{aligned}
\oint_{C} \vec{B} \cdot \overrightarrow{d l} &=\int_{0}^{2 \pi}|\vec{B}| \vec{e}_{\varphi} \cdot \vec{e}_{\varphi^{r}} d \varphi \\
&=|\vec{B}| r \int_{0}^{2 \pi} d \varphi \\
&=|\vec{B}| r 2 \pi
\end{aligned}
$$
and
$$
\mu_{0} \int_{S} \vec{J} \overrightarrow{d S}=\mu_{0} I_{\text {wire }}
$$
we obtain
$$
|\vec{B}|=\frac{\mu_{0} I_{\text {wire }}}{r 2 \pi}
$$
Therefore
\begin{qt}
\begin{equation}
\vec{B}(\vec{r})=\frac{\mu_{0} q|\vec{v}|}{2 \pi r} \vec{e}_{\varphi}
\end{equation}
where $\vec{e}_{\varphi}$ is a unit vector always pointing tangential to the contour.
\end{qt}
The direction in which it circles can be determined by the so-called "right hand rule". If your thumb points in the direction of the current, the remaining fingers curl in the direction of the magnetic field.

There is also a Poisson equation for the magnetic potential:
\begin{equation}
\nabla^{2} \vec{A}=-\mu_{0} \vec{J}
\end{equation}
The Poisson equation for the vector potential can then be derived by rewriting the magnetic field in terms of the potential: $\vec{B}=\nabla \times \vec{A}$. This yields $\mu_{0} \vec{J}=\nabla \times \vec{B}=\nabla \times \nabla \times \vec{A} .$ Then, we can rewrite this using the identity
$$
\nabla \times \nabla \vec{A}=\nabla(\nabla \vec{A})-\nabla^{2} \vec{A}
$$
To simplify this further, we can use the observation that potentials cannot be directly measured and only potential differences can. Hence, we can always add a constant to our potentials, and this so-called gauge freedom can be used to achieve \textbf{$\nabla\cdot\vec{A}=0$}.If we use the gauge freedom like this, we get the poisson equation above. The general solution can be derived again using the Green’s function method and reads
\begin{equation}
\vec{A}_{\mathrm{sol}}(\vec{r})=\frac{\mu_{0}}{4 \pi} \int \frac{\vec{J}\left(\vec{r}^{\prime}\right)}{\left|\vec{r}-\vec{r}^{\prime}\right|} d^{3} r^{\prime}
\end{equation}
\section{Electrodynamics}
\subsection{General Solution of the Wave Function}
The most basic solutions of the electric wave equations look like
\begin{qt}
\textbf{Plane wave solution}
\begin{equation}
\vec{E}=\vec{E}_{0} \cos (\vec{k} \cdot \vec{r} \pm \omega t+\delta)
\end{equation}
where $\vec{k}$ is a vector that determines in which direction the wave is traveling and $\delta$ encodes possible phase shifts.

Moreover, $\vec{E}_{0}$ is a vector whose magnitude $\left|\vec{E}_{0}\right|$ describes the amplitude of the wave and its direction determines the direction in which the electric field oscillates. The choice of the $\operatorname{sign} \pm$ in the cosine function determines whether the wave travels in the positive direction or negative direction on the axis defined by $\vec{k}$.
\end{qt}
we can use sums of the basic plane wave solutions to create more complicated solutions. A simple example is a \textbf{standing wave}:
\begin{qt}
\begin{equation}
\vec{E}=\overrightarrow{E_{0}}(\cos (\vec{k} \cdot \vec{r}-\omega t)+\cos (\vec{k} \cdot \vec{r}+\omega t))=\vec{E}_{0}(\cos (\vec{k} \cdot \vec{r}) \cos (\omega t))
\end{equation}
The crucial point is that the spatial dependence $\vec{k} \cdot \vec{r}$ of the wave is \redp{completely separated from the time dependence $\omega t$. This means that the spatial shape of the wave is fixed and does not change as time moves on.} However, since we are still multiplying this fixed form of the wave by $cos(\omega t)$, \textbf{the amplitude of the wave at each point still varies (but not the wave form).}
\end{qt}

In particular, the most general solution of the wave equation is linear combination of all possible plane waves:
\begin{qt}
\begin{equation}
\vec{E}(\vec{r}, t)=\int_{-\infty}^{\infty} \frac{d^{3} k}{2 \pi^{3}} \vec{E}(\vec{k}) \cos (\vec{k} \cdot \vec{r}-\omega t)
\end{equation}
\end{qt}

\subsection{Basic properties of electromagnetic waves}
1. The argument $\varphi \equiv(\vec{k} \cdot \vec{r} \pm \omega t)$ of our periodic function $\cos \varphi$ is called the \textbf{phase} of the wave.

2. The vector $\vec{k}$ is usually called the wave vector. The direction of $\vec{k}$ tells us in which direction the wave is traveling. \textbf{\bluep{The length of the wave vector $|\vec{k}|$ describes how many oscillations there are per meter.}} To understand this, imagine that we could stop the time, i.e. keep $t$ fixed and then move through space. As we move along the axis defined by $\vec{k}$ we count how many full wave shapes we encounter per meter. This number is the wave number. One full oscillation is over as soon as the phase of the wave has increased by $2\pi$. Hence, we can say a bit more precisely that $|\vec{k}|$ measures how many $2\pi$ cycles there are per meter. For this reason, $|\vec{k}|$ is known as spatial angular frequency or \textbf{wave number}.

For example, if we move 2 meters and observe that the phase changes by 20$\pi$, we know that the wave number is 10$\pi$ radians per meter. The wave number is directly related to the \textbf{wavelength}:
\begin{equation}
\lambda=\frac{2 \pi}{|\vec{k}|}
\end{equation}

3. The constant $\omega$ is known as temporal angular frequency or simply angular frequency. The angular frequency describes how many oscillations there are per second. 

4. The direction in which the amplitude vector $\vec{E}_{0}$ points, \bluep{\textbf{specifies the geometrical orientation of the oscillation.}} Usually, the direction of $\vec{E}_{0}$ is called the \textbf{polarization} of the wave. The length of the amplitude vector $\left|\vec{E}_{0}\right|$ encodes the peak magnitude of the oscillation.An extremely important observation is that \redp{the amplitude vector cannot point in any arbitrary direction for electromagnetic waves}.According to Gauss's law, \bluep{\textbf{The electromagnetic waves cannot be polarized in the direction they are traveling.}}

5. The sign between the two terms in the cosine function determines whether our wave moves up or down on the axis defined by $\vec{k}$.

6.The absolute phase $\delta$ encodes the phase of the wave at $\vec{r}=0$ and $t=0$.

\subsection{Advanced Properties of electromagnetic waves}
\begin{mybox}
\textbf{1. How fast are electromagnetic waves traveling?}
\end{mybox}
\begin{mybox2}
\begin{center}
    


\tikzset{every picture/.style={line width=0.75pt}} %set default line width to 0.75pt        

\begin{tikzpicture}[x=0.75pt,y=0.75pt,yscale=-1,xscale=1]
%uncomment if require: \path (0,300); %set diagram left start at 0, and has height of 300

%Shape: Axis 2D [id:dp7025483613163162] 
\draw [line width=1.5]  (14.55,141.78) -- (449.55,141.78)(63.13,73.87) -- (63.13,204.13) (442.55,136.78) -- (449.55,141.78) -- (442.55,146.78) (58.13,80.87) -- (63.13,73.87) -- (68.13,80.87)  ;
%Shape: Wave [id:dp27048813912735015] 
\draw  [line width=1.5]  (63,142.57) .. controls (67.16,168.92) and (71.14,194) .. (75.67,194) .. controls (80.19,194) and (84.01,168.92) .. (88,142.57) .. controls (91.99,116.22) and (95.81,91.13) .. (100.33,91.13) .. controls (104.86,91.13) and (108.84,116.22) .. (113,142.57) .. controls (117.16,168.92) and (121.14,194) .. (125.67,194) .. controls (129.14,194) and (132.19,179.25) .. (135.22,160.49) ;
%Shape: Circle [id:dp34174852772474684] 
\draw  [color={rgb, 255:red, 227; green, 26; blue, 26 }  ,draw opacity=1 ][fill={rgb, 255:red, 235; green, 20; blue, 20 }  ,fill opacity=1 ] (105,111.7) .. controls (105,109.66) and (106.66,108) .. (108.7,108) .. controls (110.74,108) and (112.4,109.66) .. (112.4,111.7) .. controls (112.4,113.74) and (110.74,115.4) .. (108.7,115.4) .. controls (106.66,115.4) and (105,113.74) .. (105,111.7) -- cycle ;
%Shape: Wave [id:dp9863105582782391] 
\draw  [line width=1.5]  (314,141.57) .. controls (318.16,167.92) and (322.14,193) .. (326.67,193) .. controls (331.19,193) and (335.01,167.92) .. (339,141.57) .. controls (342.99,115.22) and (346.81,90.13) .. (351.33,90.13) .. controls (355.86,90.13) and (359.84,115.22) .. (364,141.57) .. controls (368.16,167.92) and (372.14,193) .. (376.67,193) .. controls (380.14,193) and (383.19,178.25) .. (386.22,159.49) ;
%Shape: Circle [id:dp568020489264297] 
\draw  [color={rgb, 255:red, 227; green, 26; blue, 26 }  ,draw opacity=1 ][fill={rgb, 255:red, 235; green, 20; blue, 20 }  ,fill opacity=1 ] (356,111.7) .. controls (356,109.66) and (357.66,108) .. (359.7,108) .. controls (361.74,108) and (363.4,109.66) .. (363.4,111.7) .. controls (363.4,113.74) and (361.74,115.4) .. (359.7,115.4) .. controls (357.66,115.4) and (356,113.74) .. (356,111.7) -- cycle ;
%Straight Lines [id:da5601183359970614] 
\draw  [dash pattern={on 4.5pt off 4.5pt}]  (112.4,111.7) -- (356,111.7) ;


%Right Arrow [id:dp8134346999842936] 
\draw   (187,67.37) -- (232.55,67.37) -- (232.55,54.2) -- (257,74.2) -- (232.55,94.2) -- (232.55,81.03) -- (187,81.03) -- cycle ;
%Right Arrow [id:dp6775378250281021] 
\draw   (264.55,262.37) -- (289.55,262.37) -- (289.55,254.37) -- (310,268.28) -- (289.55,282.2) -- (289.55,274.2) -- (264.55,274.2) -- cycle ;

% Text Node
\draw (125,123) node    {$x_{1}$};
% Text Node
\draw (376,122) node    {$x_{2}$};
% Text Node
\draw (417,158) node    {$X$};
% Text Node
\draw (167,73.2) node    {$t_{1}$};
% Text Node
\draw (278,73.2) node    {$t_{2}$};
% Text Node
\draw (252,223.2) node   [align=left] {Following a specific point on wave, \\the phase of the point remains the same:};
% Text Node
\draw (177,267.2) node    {$kx_{1} -wt_{1} =kx_{2} -wt2$};
% Text Node
\draw    (314.5,245.2) -- (419.5,245.2) -- (419.5,285.2) -- (314.5,285.2) -- cycle  ;
\draw (367,265.2) node    {$v=\frac{x_{2} -x_{1}}{t_{2} -t_{1}} =\frac{w}{k}$};


\end{tikzpicture}

\end{center}
\end{mybox2}
\bluep{In words, the velocity of each point in our wave form is given by the ratio of the angular frequency $\omega$ and the wave number $k$}. From a different perspective, a velocity has units meter per second. The only combination of our basic wave quantities gives such unit is 
$$
v=\frac{\lambda}{\tau}
$$
In words, this equation tells us that a wave travels one wavelength $\lambda$ per period $\tau .$ We can rewrite the velocity of the wave in terms of the angular frequency $\omega$ and wave number $k\equiv|\vec{k}|$ as follows:
\begin{qt}
\begin{equation}
v=\frac{\lambda}{\tau}=\frac{2 \pi / k}{2 \pi / \omega}=\frac{\omega}{k}
\end{equation}
\end{qt}

2. If we put the general form of the solution in (\ref{waveEqElectric}), we obtain:
\begin{qt}
\textbf{the dispersion relation}
\begin{equation}
k^{2}=\mu_{0} \epsilon_{0} \omega^{2}
\label{dispersion}
\end{equation}
And we have
\begin{equation}
\frac{\omega}{k}=\sqrt{\frac{1}{\mu_{0} \epsilon_{0}}}
\end{equation}
Putting the experimental values, we find the \textbf{speed of light}:
\begin{equation}
c \equiv 2.9979 \times 10^{8} \mathrm{m} / \mathrm{s}
\end{equation}
\end{qt}

3. Let's now derive \redp{\textbf{Poynting theorem}}, which is analogous to the continuity equation. And Poynting theorem proves that \textbf{\redp{electromagnetic wave carries energy.}}

Using the Lorentz force law, we can calculate the work done by the electromagnetic field on a single charge $q$ is:
$$
\vec{F} \cdot d \vec{l}=q(\vec{E}+\vec{v} \times \vec{B}) \cdot \vec{v} d t=q \vec{E} \cdot \vec{v} d t
$$
To calculate the work done on all charges, we use $q=\rho d V$ and $\vec{J}=\rho \vec{v} .$ The rate at which work is done on all charges is therefore
\begin{equation}
    \frac{d W}{d t}=\int_{V}(\vec{E} \cdot \vec{J}) d V
    \label{powerPerVol}
\end{equation}


So, $\vec{E} \cdot \vec{J}$ is \textbf{the power per unit volume.} If we use Maxwell's equation to rewrite this power, we have:
$$
\vec{E} \cdot \vec{J}=\frac{1}{\mu_{0}} \vec{E} \cdot(\vec{\nabla} \times \vec{B})-\epsilon_{0} \vec{E} \cdot \frac{\partial \vec{E}}{\partial t}
$$
Since
\begin{qt}
\begin{equation}
\nabla \cdot(\vec{E} \times \vec{B})=\vec{B} \cdot(\vec{\nabla} \times \vec{E})-\vec{E} \cdot(\vec{\nabla} \times \vec{B})
\end{equation}
and
\begin{equation}
\frac{\partial}{\partial t} \vec{B}^{2}=\left(\frac{\partial}{\partial t} \vec{B}\right) \vec{B}+\vec{B}\left(\frac{\partial}{\partial t} \vec{B}\right)= 2 \vec{B} \frac{\partial}{\partial t} \vec{B}
\end{equation}
\end{qt}
we have
\begin{equation}
\begin{aligned}
\vec{E} \cdot \vec{J}&=\frac{1}{\mu_{0}}(\vec{B} \cdot(\vec{\nabla} \times \vec{E})-\nabla \cdot(\vec{E} \times \vec{B}))-\epsilon_{0} \vec{E} \cdot \frac{\partial \vec{E}}{\partial t}\\
&=\frac{1}{\mu_{0}} \vec{B} \cdot\left(-\frac{\partial}{\partial t} \vec{B}\right)-\frac{1}{\mu_{0}} \nabla \cdot(\vec{E} \times \vec{B})-\epsilon_{0} \vec{E} \cdot \frac{\partial \vec{E}}{\partial t}\\
&=-\frac{1}{2 \mu_{0}} \frac{\partial}{\partial t} \vec{B}^{2}-\frac{1}{\mu_{0}} \nabla \cdot(\vec{E} \times \vec{B})-\epsilon_{0} \frac{1}{2} \frac{\partial}{\partial t} \vec{E}^{2}
\end{aligned}
\end{equation}
Putting this into Eq.\ref{powerPerVol} yields
\begin{equation}
\begin{aligned}
\frac{d W}{d t} &=\int_{V}(\vec{E} \cdot \vec{J}) d V \\
&=\int_{V}\left(-\frac{1}{2 \mu_{0}} \frac{\partial}{\partial t} \vec{B}^{2}-\frac{1}{\mu_{0}} \nabla \cdot(\vec{E} \times \vec{B})-\epsilon_{0} \frac{1}{2} \frac{\partial}{\partial t} \vec{E}^{2}\right) d V \\
&\left.=-\frac{1}{2} \frac{\partial}{\partial t} \int_{V}\left(\frac{1}{\mu_{0}} \vec{B}^{2}+\epsilon_{0} \vec{E}^{2}\right)\right) d V-\int_{V} \frac{1}{\mu_{0}} \nabla \cdot(\vec{E} \times \vec{B}) d V \\
&=-\frac{1}{2} \frac{\partial}{\partial t} \int_{V}\left(\frac{1}{\mu_{0}} \vec{B}^{2}+\epsilon_{0} \vec{E}^{2}\right) d V-\oint_{S} \frac{1}{\mu_{0}}(\vec{E} \times \vec{B}) \cdot d \vec{a} \\
& \equiv-\frac{d U_{\mathrm{em}}}{d t}-\oint_{S} \vec{S} \cdot d \vec{a}
\end{aligned}
\end{equation}
\begin{qt}
Thus, the Poynting theorem reads:
\begin{equation}
    \frac{d W}{d t}=-\frac{d U_{\mathrm{em}}}{d t}-\oint_{S} \vec{S} \cdot d \vec{a}
\end{equation}
Where
\begin{equation}
\vec{S} \equiv \frac{1}{\mu_{0}}(\vec{E} \times \vec{B})
\end{equation}
is usually called the \textbf{\redp{Poynting vector}}. Moreover, $U_{\mathrm{em}}$ is the total energy stored in the electromagnetic field configuration.
\end{qt}
The Poynting theorem tells us that the work done on charges by the Lorentz force is equal to the decrease in energy stored in the field $\frac{d U_{\mathrm{em}}}{d t}$ minus the energy which has flowed through the surface $S .$ In other words, \textbf{if the energy stored in the electromagnetic field gets smaller, it must have either been used to move charges around $\left(\frac{d W}{d t}\right)$ or has flown out of the volume we are considering $\left(\oint_{S} \vec{S} \cdot d \vec{a}\right) .$}

We can make the analogy between Poynting theorem and continuity equation more concrete by introduce the mechanical energy density:
$$
\frac{d W}{d t} \equiv \frac{d}{d t} \int_{V} u_{\mathrm{mech}} d V
$$
where
$$
u_{\mathrm{em}} \equiv \frac{1}{2}\left(\epsilon_{0} \vec{E}^{2}+\frac{1}{\mu_{0}} \vec{B}^{2}\right)
$$
Thus,
$$
\begin{aligned}
\frac{d W}{d t} &=-\frac{d U_{\mathrm{em}}}{d t}-\oint_{S} \vec{S} \cdot d \vec{a} \\
\frac{d}{d t} \int_{V} u_{\mathrm{mech}} d V &=-\frac{d}{d t} \int_{V} u_{\mathrm{em}} d V-\oint_{S} \vec{S} \cdot d \vec{a}
\end{aligned}
$$
and \textbf{the differential form of Poynting theorem is}
$$
\frac{d}{d t}\left(u_{\mathrm{mech}}+u_{\mathrm{em}}\right)=-\nabla \cdot \vec{S}
$$
\begin{mybox}
\textbf{4. How can we produce changing field configuration?}
\end{mybox}
\begin{mybox2}
\textbf{Through accelerating charges}
\end{mybox2}

\section{Gauge Symmetry}
Gauge symmetry refers to the observation that we can't measure potentials like the electric potential $A_{0}$ or the magnetic potential $\vec{A}$ directly.\textbf{ The electric and magnetic field strengths remain completely unchanged if we shift our potentials by a constant amount}:
$$
\begin{array}{l}
{A_{0} \rightarrow A_{0}+\eta} \\
{A_{i} \rightarrow A_{i}+\xi_{i}}
\end{array}
$$
Thus,
\begin{qt}
\begin{equation}
\begin{aligned}
E_{i}=-\partial_{i} A_{0}-\partial_{0} A_{i} \rightarrow \tilde{E}_{i} &=-\partial_{i}\left(A_{0}+\eta\right)-\partial_{0}\left(A_{i}+\xi_{i}\right) \\
&=-\partial_{i} A_{0}-\underbrace{\partial_{i} \eta}_{=0}-\partial_{0} A_{i}-\underbrace{\partial_{0} \xi}_{=0} \\
&=-\partial_{i} A_{0}-\partial_{0} A_{i} \\
&=E_{i} 
\end{aligned}
\end{equation}
and
\begin{equation}
\begin{aligned}
B_{i}=\epsilon_{i j k} \partial_{j} A_{k} \rightarrow B_{i} &=\epsilon_{i j k} \partial_{j}\left(A_{k}+\xi_{k}\right) \\
&=\epsilon_{i j k} \partial_{j} A_{k}+\epsilon_{i j k} \partial_{j} \xi_{k} \\
&=\epsilon_{i j k} \partial_{j} A_{k} \\
&=B_{i} 
\end{aligned}
\end{equation}
\end{qt}
\redp{More importantly, We can not only add constants to the potentials but also derivatives of an arbitrary scalar function \textbf{$\eta(t,\vec{x})$}}:
\begin{qt}
\textbf{Gauge Freedom/gauge symmetry}
\begin{equation}
\begin{array}{l}
{A_{0} \rightarrow A_{0}+\partial_{0} \eta(t, \vec{x})} \\
{A_{i} \rightarrow A_{i}+\partial_{i} \eta(t, \vec{x})}
\end{array}
\end{equation}
\end{qt}
We can check this as:
$$
\begin{aligned}
E_{i}=-\partial_{i} A_{0}-\partial_{0} A_{i} \rightarrow \tilde{E}_{i} &=-\partial_{i}\left(A_{0}+\partial_{0} \eta(t, \vec{x})\right)-\partial_{0}\left(A_{i}+\partial_{i} \eta(t, \vec{x})\right) \\
&=-\partial_{i} A_{0}-\partial_{i} \partial_{0} \eta(t, \vec{x})-\partial_{0} A_{i}-\partial_{0} \partial_{i} \eta(t, \vec{x}) \\
&=-\partial_{i} A_{0}-\partial_{0} \partial_{i} \eta(t, \vec{x})-\partial_{0} A_{i}-\partial_{0} \partial_{i} \eta(t, \vec{x}) \\
&=-\partial_{i} A_{0}-\partial_{0} A_{i}=E_i
\end{aligned}
$$
and
$$
\begin{aligned}
\tilde{B}_{i} &=\epsilon_{i j k} \partial_{j}\left(A_{k}+\partial_{k} \eta(t, \vec{x})\right) \\
&=\epsilon_{i j k} \partial_{j} A_{k}+\underbrace{\epsilon_{i j k} \partial_{j} \partial_{k} \eta(t, \vec{x})}_{=0} \\
&=\epsilon_{i j k} \partial_{j} A_{k}=B_i
\end{aligned}
$$
where we used that \bluep{$\epsilon_{i j k}$ is antisymmetric but $\partial_{j} \partial_{k}$ is symmetric under the switching of the indices $j \leftrightarrow k .$}
\begin{mybox}
\textbf{How to choose a gauge so that $\nabla \cdot \vec{A}=0$ (Coulomb Gauge)}?
\end{mybox}
\begin{mybox2}
The modified potential reads:
$$
\vec{A}^{\prime}=\vec{A}+\nabla \eta(t, \vec{x})
$$
The divergence of this reads
$$
\begin{aligned}
\nabla \cdot \vec{A}^{\prime}(t, \vec{x}) &=\nabla \cdot \vec{A}(t, \vec{x})+\nabla \cdot \nabla \eta(t, \vec{x}) \\
&=f(t, \vec{x})+\nabla \cdot \nabla \eta(t, \vec{x})
\end{aligned}
$$
By solving the following equation:
$$
\nabla \cdot \nabla \eta_{\mathrm{sol}}(t, \vec{x})=-\nabla \cdot f(t, \vec{x})
$$
we can find our Coulomb gauge. In practice, we don't have to find the function explicitly, but instead can simply use the knowledge that a function with the required properties exists and set $\nabla \cdot \vec{A}=0$.
\end{mybox2}

\subsection{Electrodynamics as a gauge theory}
\subsubsection{Financial toy system}
Here we use a simple financial toy system to show the definition of gauge redundancy and symmetry. And the difference that active/passive transformation made to the toy system. 

we now introduce independent local currencies in, say Germany, which we call Deutsche Mark (DM). Moreover, we introduce Francs (F) in France, in England Pounds (P) and Lira (L) in Italy. The exchange rates are
$$
\begin{aligned}
D M / P &=1 \\
P / F &=2 \\
F / L &=10 \\
D M / L &=20
\end{aligned}
$$
When a local currency changes, the bookkeepers simply adjust their exchange rates accordingly and the situation remains the same. Thanks to these bookkeepers, we can see that such passive transformations really make no difference as it should be.\bluep{Our bookkeeper aren't dynamical actors which start actions on their own. They do not have any physical influence on the dynamics of the system.}

The change in the local currency is an example of \redp{invariance under passive transformations}. It is called as a \textbf{\redp{redundancy}}. An invariance under active transformations is called a \textbf{\redp{symmetry}}. The redundancy that exists in our description of the financial toy example after the introduction of the bookkeepers is an example of a \textbf{\redp{local gauge symmetry.}}
\subsubsection{Gauge dynamics}
So far, our bookkeepers are purely mathematical ingredients which we introduced to make our description invariant under local passive transformations. Let's now imagine the exchange rates set by the bank as:
$$
\begin{aligned}
D M / P &=1 \\
P / F &=2 \\
F / L &=10 \\
D M / L &=10
\end{aligned}
$$
Now our trader is able to earn money simply by exchanging money. If he starts with 1DM, he can trade it for 1P, then use the pound to trade it for 2F, then trade these for 20L and finally trade these for 2DM. In the financial world this is known as an \textbf{arbitrage opportunity}

\bluep{If there is a change in the local money coordinate system, for examole $L \rightarrow \tilde{L}=L / 10$}, we have to adjust the exchange rates accordingly as:
$$
\begin{aligned}
&F / \tilde{L}=F /(L / 10)=1\\
&D M / \tilde{L}=D M /(L / 10)=1
\end{aligned}
$$
\bluep{However, the amount of money our trader earns is unchanged by such a re-scaling}. If he starts again with 1DM, he can still trade it for 1P, which he can trade for 2F, then trade these for 2L and finally trade these for 2DM. The final result is the same as before.

\redp{Here we show a crucial aspect of gauge theory: an important task is to find quantities which do not depend on local conventions.}

There is another way to make risk-free money which involves interest rates. Let's assume that the interest rate is $2 \%$ per year for the Deutsche Mark. Moreover, we assume that the exchange rate changes over time and is now
$$
D M / L=10
$$
and in one year
$$
D M / L=5
$$
Our trader can borrow 1DM and after 1 year he has to pay 1.02DM back. Moreover, he can now exchange his 1DM for 10L. After one year he can then exchange his 10L for 2DM. Therefore, after paying back the 1.02DM he has made 0.98DM in profit.

\bluep{Promoting bookkeepers to dynamical objects which follow their own rules is a crucial step to make our toy model more realistic.}

\subsubsection{Mathematical description of the toy model}
Mathematically, we imagine that some countries live on a lattice. Each point on the lattice is labelled by $d$ -numbers: $\vec{n}=$ $\left(n_{1}, n_{2}, \cdots, n_{d}\right) .$ In other words, each country can be identified by a vector $\vec{n}$ which points to its location. We can move from one country to a neighboring country by using a basis vector $\vec{e}_{i},$ where $i$ denotes the direction we are moving. For example, $\vec{e}_{2}=(0,1,0 \cdots, 0)$

We denote the \textbf{currency exchange rates} between the country labelled by the vector $\vec{n}$ and its neighbor in the $i$ -direction by $R_{\vec{n}, i}$. For example, if the country at the location labelled by $\vec{n}$ uses Deutsche Marks and its neighbor in the 2 -direction uses Francs, $R_{\bar{n}, 2}$ tells us how many Francs we get for each Deutsche Mark. 

In physics, we usually introduce the corresponding logarithms
$$
R_{\vec{n}, i} \equiv e^{A_{i}(\vec{n})}
$$
where $A_{i}(\vec{n}) \equiv \ln \left(R_{\vec{n}, i}\right)$.

We use the notation $f(\vec{n})$ to denote a change of the currency in the country at $\vec{n}$ by a factor of $f(\vec{n}) .$ In addition, we again introduce the corresponding logarithm
$$
f(\vec{n}) \equiv e^{\varepsilon(\vec{n})}
$$
In general, when we perform such a gauge transformation in the country labelled by $\vec{n}$ and also in the neighboring country in the $i$ -direction, the corresponding exchange rate changes as follows:
$$
\begin{aligned}
R_{\vec{n}, i}=e^{A_{i}(\vec{n})} \rightarrow & \frac{f_{\vec{n}}+\vec{e}_{i}}{f_{\vec{n}}} R_{\vec{n}, i} \\
&=\frac{e^{\epsilon\left(\vec{n}+\vec{e}_{i}\right)}}{e^{\epsilon(\vec{n})}} e^{A_{i}(\vec{n})} \\
&=e^{A_{i}(\vec{n})+\epsilon\left(\vec{n}+\vec{e}_{i}\right)-\epsilon(\vec{n})}
\end{aligned}
$$
Thus, we conclude
$$
A_{i}(\vec{n}) \rightarrow A_{i}(\vec{n})+\epsilon\left(\vec{n}+\vec{e}_{i}\right)-\epsilon(\vec{n})
$$
An arbitrage opportunity exists when we can trade currencies in such a way that we end up with more money than we started with. But we can only make such a statement when the starting currency and the final currency are the same. \textbf{The total gain we can earn by following a specific loop can be quantified by the \bluep{gain factor}}
$$
G=R_{\vec{n}, i} R_{\vec{n}+\vec{e}_{i}, j} \frac{1}{R_{\vec{n}+\vec{e}_{j}, i}} \frac{1}{R_{\vec{n}, j}}
$$
When this gain factor is larger than one, we can earn money by trading money following the loop. Once more we introduce the corresponding logarithm
$$
G \equiv e^{F_{i j}(\vec{n})}
$$
and
$$
F_{i j}(\vec{n})=A_{j}\left(\vec{n}+\vec{e}_{i}\right)-A_{j}(\vec{n})-\left[A_{i}\left(\vec{n}+\vec{e}_{j}\right)-A_{i}(\vec{n})\right]
$$
A crucial consistency check is that $G$ and $F_{i j}$ are unchanged by gauge transformations. Quantities like this are usually called \textbf{gauge invariant}. Moreover, an important technical observation is that $F_{i j}(\vec{n})$ is antisymmetric: $F_{i j}(\vec{n})=-F_{j i}(\vec{n}),$ which follows directly from thdefinition.

Now let's introduce \bluep{temporal exchange rate} by specifying a point on the lattice using $d+1$ coordinates $\vec{n}=(n_0,n_1,....)$, where the zeroth component indicates the point in time. Thus,
\begin{equation}
F_{\mu \nu}(\vec{n})=A_{\mu}\left(\vec{n}+\vec{e}_{\mu}\right)-A_{v}(\vec{n})-\left[A_{\mu}\left(\vec{n}+\vec{e}_{v}\right)-A_{\mu}(\vec{n})\right]
\end{equation}
In the continuum limit,
\begin{qt}
\begin{equation}
\begin{aligned}
&A_{\mu}\left(x_{\mu}\right) \rightarrow A_{\mu}\left(x_{\mu}\right)+\frac{\partial \epsilon}{\partial x^{\mu}}\\
&F_{\mu \nu}\left(x_{\mu}\right) \equiv \frac{\partial A_{\nu}}{\partial x^{\mu}}-\frac{\partial A_{\mu}}{\partial x^{\nu}}
\end{aligned}
\end{equation}
\end{qt}
\bluep{We can not only earn money by trading money itself, but also by trading goods like, for example, copper.} Depending on the local prices it can be lucrative to buy copper in one country and sell it in another country. The gain factor for such process is given by:
\begin{equation}
g=\frac{p\left(\vec{n}+\vec{e}_{i}\right)}{p(\vec{n}) R_{\vec{n}, i}}
\end{equation}
where $p(\vec{n})$ is the price of copper at $\vec{n}$. Again, we introduce the corresponding logarithm
\begin{equation}
g \equiv e^{J_{i}(\bar{n})}
\end{equation}
and
\begin{equation}
\begin{aligned}
&e^{J_{i}(\vec{n})}=\frac{e^{\varphi\left(\vec{n}+\vec{e}_{i}\right)}}{e^{\varphi(\vec{n})} e^{A_{i}(\vec{n})}}\\
&J_{i}(\vec{n})=\varphi\left(\vec{n}+\vec{e}_{i}\right)-\varphi(\vec{n})-A_{i}(\vec{n})
\end{aligned}
\end{equation}
The amount of money we earn depends on the amount of copper $q$ we carry around. Thus,
\begin{equation}
J_{\mu}(\vec{n})=q\left(\varphi\left(\vec{n}+\vec{e}_{\mu}\right)-\varphi(\vec{n})-A_{\mu}(\vec{n})\right)
\end{equation}
\bluep{In the trade described by $J_{i}(\vec{n}),(i=1,2,3)$ copper is transported from the country at $\vec{n}$ to the neighboring country at $\vec{n}+\vec{e}_{i} .$ Hence, $J_{i}(\vec{n})$ is a measure of the amount of copper that flows between the two countries. $J_{0}(\vec{n})$ tells us how much money we can earn by buying copper and selling it at a later point in time in the \textbf{same country}.} 
\subsubsection{Gauge rules}
we start with the crucial assumption that copper is conserved (i.e. no copper is destroyed or produced). And it must be true that:\redp{change of amount of copper in country $\vec{n}=$ total net flow}:
\begin{equation}
J_{0}\left(\vec{n}+\vec{e}_{0}\right)-J_{0}(\vec{n})=-\left(\sum_{i=1}^{d} J_{i}(\vec{n})-\sum_{i=1}^{d} J_{i}\left(\vec{n}-\vec{e}_{i}\right)\right)
\end{equation}
In the continuum limit, we get continuity equation:
\begin{qt}
\begin{equation}
\sum_{\mu=0}^{3} \partial_{\mu} J_{\mu}=0
\end{equation}
\end{qt}
Moreover, we already know that the good quantities to describe our system are $J_{\mu}$ and $F_{\mu \nu}$ since these do not depend on local conventions. The quantities $J_{\mu}$ contain information about the positions and flow of copper, while $F_{\mu \nu}$ represent arbitrage opportunities. $F_{\mu\nu}$ is \redp{anti-symmetric} and $\partial_{\mu} \partial_{\nu}=\partial_{\nu} \partial_{\mu}$,so 
\begin{equation}
\sum_{\mu=0}^{3} \sum_{v=0}^{3} \partial_{v} \partial_{\mu} F_{\mu v}=0
\end{equation}
From here, we obtain the famous \redp{\textbf{inhomogeneous Maxwell equation}} as:
\begin{equation}
    \sum_{v=0}^{3} \partial_{v} F_{\mu v}=\mu_{0} J_{\mu}
\end{equation}
and
\begin{equation}
\sum_{v=0}^{3} \sum_{v=0}^{3} \partial_{\mu} \partial_{v} F_{\mu v}=\mu_{0} \sum_{v=0}^{3} \partial_{\mu} J_{\mu}
\end{equation}
\textbf{\redp{Gauss's law}} can be written as:
\begin{equation}
\sum_{i=0}^{3} \partial_{i} F_{0 i}=\mu_{0} J_{0}
\end{equation}

\bluep{To summarize: quantum mechanics and electrodynamics are invariant under active global gauge transformations. Hence, the global gauge symmetry is a real symmetry. However, only our description is invariant under passive local transformations. Therefore, local gauge symmetry is a redundancy.}

In particular, this means that whenever we perform a local passive transformation, we have to accompany:
\begin{equation}
\Psi \rightarrow \mathrm{e}^{i \varepsilon(x)} \Psi
\end{equation}
always with
\begin{equation}
A_{\mu} \rightarrow A_{\mu}+\partial_{\mu} \epsilon(x)
\end{equation}
When we perform a passive transformation these two transformations always go hand in hand. In contrast, there is no need to change $A_{\mu}$ if we only have global gauge transformation:
$$
A_{\mu}(x) \rightarrow A_{\mu}(x)+a_{\mu}
$$
in electrodynamics, and
$$
\Psi(x) \rightarrow \mathrm{e}^{i \varepsilon} \Psi(x)
$$
in quantum mechanics.